---
title: "Plotting Tools"
author: "Christopher Prener"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`prener` includes a number of functions that I use in conjunction with `ggplot2`. The package includes a tool for implementing points as a unit of measure in `ggplot2` as well as standardized export options.

## Sizing Plots
One issue I address is that `ggsave()` does not accept measurements for `width` and `height` in points, but Keynote lays slides out using points as the unit of measurement. The `cp_points()` function will convert points to inches, centimeters, or millimeters (the units used by `ggsave()`).

```{r}
cp_points(200, units = "in")
cp_points(200, units = "cm")
cp_points(200, units = "mm")
```

These functions can be embedded directly in `ggsave()` calls:

```{r, eval=FALSE}
p <- ggplot(mpg, aes(hwy)) + geom_histogram()

ggsave("hwy", p, device = "png", 
       width = cp_points(500, units = "mm"), 
       height = cp_points(375, units = "mm"), 
       units = "mm", dpi = 300)
```

## Standardized Export Options

The [Keynote templates](https://github.com/chris-prener/sequoia_templates) that I use for teaching and presentations have three standard sizes that I create plots for - small (960 x 540 points), medium (960 x 630 points), and large (1024 by 768 points). The `cp_plotSave()` function will export `ggplot2` plots at these dimensions. By default, these are done at 300 dots per inch but that can also be adjusted:

```{r, eval=FALSE}
p <- ggplot(mpg, aes(hwy)) + geom_histogram()

cp_plotSave("hwy", p, preset = "sm")
cp_plotSave("hwy", p, preset = "med")
cp_plotSave("hwy", p, preset = "lg", dpi = 500)
```

If no `device` is specified, plots will be exported as `.png` files. Other output options may be specified using `device`:

```{r, eval=FALSE}
cp_plotSave("hwy", p, device = "pdf", preset = "lg", dpi = 500)
```
